A Search for Circumstellar Companions Around Nearby White Dwarf Sirius b

### 2021-07-20 paper/paper.tex
update paper

\documentclass[RNAAS]{aastex631}
\usepackage{hyperref}
\let\tablenum\relax
\usepackage[output-exponent-marker = \text{e}]{siunitx}

@@

@@

\section{}

% \acknowledgments

% \software{
% astropy \citep{2013A&A...558A..33A,2018AJ....156..123A},
% numpy \citep{harris2020array},
% scikit-image \citep{2014arXiv1407.6245V},
% }

>>>>

\documentclass[twocolumn]{aastex631}
\usepackage{hyperref}
\let\tablenum\relax
\usepackage[output-exponent-marker = \text{e}]{siunitx}

\DeclareSIUnit\parsec{pc}
\DeclareSIUnit\au{AU}
\DeclareSIUnit\mj{M_J}
\DeclareSIUnit\year{yr}

@@

\shorttitle{A Search for Circumstellar Companions around Sirius b}
\shortauthors{Lucas et al.}

@@

\section{Introduction} \label{sec:intro}

Very little is known about the evolution of planetary systems beyond the main-sequence lifetime of their host stars. Theoretical calculations show that planets can survive the red giant and asymptotic giant stages \citep{burleigh_imaging_2002,jura_pollution_2008,nordhaus_orbits_2013}, and results from radial velocity and transit surveys suggest extrasolar planets are prevalent throughout the Milky Way \citep{cumming_keck_2008}. However, only one planetary mass object has been detected around a white dwarf (WD) with imaging \citep[WD 0806-661;][]{luhman_discovery_2011}.

Directly imaging exoplanets is a powerful method in exoplanet science which explores a parameter space very complementary to the popular transit photometry and radial velocity methods. The red giant stage has cleared planets within a few \si{au} greatly lowering the transit probability. White dwarfs have very few spectral lines to make high-precision radial velocity measurements from spectral lines. Imaging, though, benefits from the orbital expansion of the planet, and the cooling of the white dwarf greatly reduces the contrast between them \citep{burleigh_imaging_2002,gould_finding_2008}. The Degenerate Objects around Degenerate Objects (DODO) survey observed 29 white dwarfs with Gemini/NIRI and VLT/ISAAC and provided upper limits around $\sim$\SI{8}{\mj} beyond \SI{35}{\au} \citep{hogan_dodo_2009}.

In this work we study the closest white dwarf to the Sun, Sirius b, and provide upper mass limits based on our observations in the near-infrared. \autoref{sec:obs} describes our target and observing strategy, \autoref{sec:analysis} describes the processing and analysis techniques used, \autoref{sec:results} describes our results and we conclude with \autoref{sec:conclusion}.

\section{Observations} \label{sec:obs}

Sirius is the closest star system to the Sun at \SI{2.7}{\parsec} away, consisting of an A1Vm star (a) and a WD with an age around \SI{225}{\mega\year} \citep{bond_sirius_2017,collaboration_gaia_2018}. There are no known planets around either star, and using constrained 3-body numerical simulations a potential companion around Sirius b would only be stable with a \SI{1.79}{\year} orbit, which corresponds to a circular orbit with \SI{1.5}{\au} separation. Sirius b has been studied in the \SI{10}{\micro\meter} regime recently by \cite{pathak_high_2021}, who achieve \SIrange[]{1.8}{3.5}{\mj} upper limits within 2 arcseconds.

We targeted Sirius b directly using Keck/NIRC2 in Lp-band across three epochs in 2020 \autoref{tbl:obs}. Due to the high proper motion and reasonable orbital motion, we started by calculating the projected offset and position angle from Sirius a based on the orbital parameters from \cite{bond_sirius_2017}. We first slewed to Sirius a, which is easy to lock onto due to its brightness \citep[-1.35 K-band magnitude;][]{bonnet-bidaud_adonis_2008}. We found that Sirius b is too dim \citep[9.01 K-band magnitude;][]{bonnet-bidaud_adonis_2008} for the adaptive optics (AO) performance necessary for coronagraphy and that the scattered light from Sirius a was detrimental to closing the AO loop when using Sirius b as a natural guide star (NGS) anyways. Therefore, we employed a unique off-axis solution, using a narrow laser-line filter for the wavefront sensor using Sirius a as the NGS and offsetting to Sirius b manually.

The scattered light from Sirius a is so strong, in fact, that radial diffraction spikes from the Keck II secondary mirror support structure are still present in the Sirius b frames, which reduced our overall observing efficiency due to discarding these frames. An example of such a diffraction spike is shown in \autoref{fig:spike}.

\begin{figure}
    \centering
    \epsscale{1}
    \plotone{spike}
    \caption{Calibrated science frame of Sirius b from 2020-02-04 epoch showing the strong scattered light effects from Sirius a.}
    \label{fig:spike}
\end{figure}

\begin{deluxetable*}{ccccc}
    % \tabletypesize{\scriptsize}
    \tablecaption{Observing parameters for the three epochs of data. All observations were carried out using the NIRC2 Lp-band filter. Observation time is based on the frames that were selected for processing.
    \label{tbl:obs}}
    \tablehead{
        \colhead{Date observed} & 
        \colhead{Observation time (hr)} & 
        \colhead{Seeing (arcsec)} & 
        \colhead{Temp (\textdegree C)} & 
        \colhead{PWV (mm)}
    }
    \startdata
    2020-02-04 & 1.44 &  &  &  \\
    2020-11-21 & 2.91 &  &  &  \\
    2020-11-28 & 2.44 &  &  &  \\
    \enddata
\end{deluxetable*}

\section{Analysis} \label{sec:analysis}

\section{Results} \label{sec:results}

\section{Conclusions} \label{sec:conclusion}

\begin{acknowledgments}

\end{acknowledgments}

\software{
ADI.jl \citep{lucas_adijl_2020},
astropy \citep{collaboration_astropy_2013,astropy_collaboration_astropy_2018},
Julia \citep{bezanson_julia_2017},
numpy \citep{harris_array_2020},
scikit-image \citep{walt_scikit-image_2014},
}
